---
title: "Oyster Meta-Analysis"
author: "Nick Ray"
date: "10/8/2020"
output: html_document
---

This code accompanies the manuscript "Meta-analysis of oyster impacts on coastal biogeochemistry" published in Nature Sustainability

Jump to:
meta-analysis and example figure code: Line 37
compare sediment fluxes between species: Line 370
compare sediment fluxes between habitats: Line 421
publication bias analysis: Line 557

Load the sediment data set first
```{r}
sed_flux = oyster_meta_excel_for_figshare
##this dataset can be donwloaded via this link: https://figshare.com/articles/dataset/Meta-analysis_of_oyster_impacts_on_coastal_biogeochemistry/12488753 

#or this link: https://doi.org/10.6084/m9.figshare.12488753 

#the dataset contains three sheets. with this code, use just the second sheet (sediment fluxes)
```


Load the necessary packages
```{r}
library(metafor)
library(meta)
library(ggplot2)
```

This meta-analysis followed these methods:
https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/#license

Test the effect of oysters on sediment N2 flux
```{r}
#use n2/ar method studies only and random effect model with Hartung-Knapp-Sidik-Jonkman method
n2_ar_sed = subset(sed_flux, n2_method == "n2_ar")

m_n2_ar <- metacont(`n N2 Oys`,
                 `Mean N2 Oys`,
                 `SD N2 Oys`,
                 `n N2 Ctrl`,
                 `Mean N2 Ctrl`,
                 `SD N2 Ctrl`,
                  data=n2_ar_sed,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_n2_ar

#print results in text file
sink("n2_ar_results_rand.txt")
print(m_n2_ar)
sink()

#####repeat for IPT
ipt_sed = subset(sed_flux, n2_method == "IPT")

m_n2_ipt <- metacont(`n N2 Oys`,
                 `Mean N2 Oys`,
                 `SD N2 Oys`,
                 `n N2 Ctrl`,
                 `Mean N2 Ctrl`,
                 `SD N2 Ctrl`,
                  data=ipt_sed,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_n2_ipt

sink("n2_IPT_results_rand.txt")
print(m_n2_ipt)
sink()

#make a nice ggplot of this
#load the plot dataset
n2_flux_fig_data_revised
#this is an excel file where I pulled the values from the meta-analysis results, with the following columns:
#column 1: "abbreviated_name" is the Abbreviated study name
#column 2: "n2_g" is the calculated study g value
#column 3: "n2_ci" is the confidence interval
#this data is also available in the Supplementary Information pdf
#here I only show the code for making one figure, but used the same approach for all sediment fluxes

n2_forest = ggplot(n2_flux_fig_data_revised, aes(x = n2_g, y = abbreviated_name, group = habitat)) +
  geom_vline(xintercept = 0, linetype = "solid")+ ###line at zero
  geom_errorbarh(aes(xmin = n2_g-n2_ci, xmax = n2_g+n2_ci), width = 0.2)+
  geom_point(aes(shape = habitat),col = "#8da0cb", size = 3)+
  theme_classic()+
  theme(axis.text.x =  element_text(size = 8,colour = "black"),
        axis.text.y =  element_text(size = 8,colour = "black"),
        axis.title.y = element_blank(),
        axis.title.x = element_text(size = 8, colour = "black"))+
  scale_x_continuous(limits = c(-2,5.5))+
  labs(x = expression(paste("N"[2]*" flux Effect (g)")))+
  geom_vline(xintercept = 0.682, linetype = "dashed")+
  annotate("text", x = 3.9, y = 13, label = "italic(g) == 0.682", parse = TRUE, size = 2.822)+
  annotate("text", x = 3.9, y = 12, label = "95%CI = \u00B1 0.276", size = 2.822)+
  annotate("text", x = 3.9, y = 11, label = "p < 0.001", size = 2.822)+
  theme(legend.position = "none")

n2_forest

###print it
ppi = 900
png("n2_forest_plot.png", width = 3.5*ppi, height = 4.5*ppi, res = ppi)
n2_forest
print(n2_forest)
dev.off()

```


Repeat for NH4
```{r}
#make table of just nh4 data
nh4_dat = sed_flux[,c(1,8,16,17,18,19,20,21)]
nh4_only = sed_flux[complete.cases(nh4_dat),]

m_nh4 <- metacont(`n NH4 Oys`,
                 `Mean NH4 Oys`,
                 `SD NH4 Oys`,
                 `n NH4 ctrl`,
                 `Mean NH4 Ctrl`,
                 `SD NH4 Ctrl`,
                  data=nh4_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_nh4

sink("nh4_results_rand.txt")
print(m_nh4)
sink()
```

And for Nox
```{r}
nox_dat = sed_flux[,c(1,8,52,53,54,55,56,57)]
nox_only = sed_flux[complete.cases(nox_dat),]

m_nox <- metacont(`n nox oys`,
                 `mean nox oys`,
                 `sd nox oys`,
                 `n nox ctrl`,
                 `mean nox ctrl`,
                 `sd nox ctrl`,
                  data=nox_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_nox

sink("nox_results_rand.txt")
print(m_nox)
sink()
```

No3-
```{r}
no3_dat = sed_flux[,c(1,8,58,59,60,61,62,63)]
no3_only = sed_flux[complete.cases(no3_dat),]

m_no3 <- metacont(`n no3 oys`,
                 `mean no3 oys`,
                 `sd no3 oys`,
                 `n no3 ctrl`,
                 `mean no3 ctrl`,
                 `sd no3 ctrl`,
                  data=no3_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_no3

sink("no3_results_rand.txt")
print(m_no3)
sink()
```

and no2-
```{r}
no2_dat = sed_flux[,c(1,8,64,65,66,67,68,69)]
no2_only = sed_flux[complete.cases(no2_dat),]

m_no2 <- metacont(`n no2 oys`,
                 `mean no2 oys`,
                 `sd no2 oys`,
                 `n no2 ctrl`,
                 `mean no2 ctrl`,
                 `sd no2 ctrl`,
                  data=no2_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_no2

sink("no2_results_rand.txt")
print(m_no2)
sink()
```


Repeat for phosphate
```{r}
po4_dat = sed_flux[,c(1,8,34,35,36,37,38,39)]
po4_only = sed_flux[complete.cases(po4_dat),]

m_po4 <- metacont(`n P Oys`,
                 `Mean P Oys`,
                 `SD P Oys`,
                 `n P Ctrl`,
                 `Mean P Ctrl`,
                 `SD P Ctrl`,
                  data=po4_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_po4

sink("po4_results_rand.txt")
print(m_po4)
sink()
```


Silica
```{r}
si_dat = sed_flux[,c(1,8,46,47,48,49,50,51)]
si_only = sed_flux[complete.cases(si_dat),]


m_si <- metacont(`n Si oys`,
                 `mean si oys`,
                 `sd Si oys`,
                 `n Si ctrl`,
                 `mean si ctrl`,
                 `sd Si ctrl`,
                  data=si_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_si

sink("si_results_rand.txt")
print(m_si)
sink()

```


N2O
```{r}
n2o_dat = sed_flux[,c(1,8,22,23,24,25,26,27)]
n2o_only = sed_flux[complete.cases(n2o_dat),]


m_n2o <- metacont(`n N2O Oys`,
                 `Mean N2O Oys`,
                 `SD N2O Oys`,
                 `n N2O Ctrl`,
                 `Mean N2O Ctrl`,
                 `SD N2O Ctrl`,
                  data=n2o_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_n2o

sink("n2o_results_rand.txt")
print(m_n2o)
sink()
```


Co2
```{r}
co2_dat = sed_flux[,c(1,8,28,29,30,31,32,33)]
co2_only = sed_flux[complete.cases(co2_dat),]

m_co2 <- metacont(`n CO2 Oys`,
                 `Mean CO2 Oys`,
                 `SD CO2 Oys`,
                 `n CO2 Ctrl`,
                 `Mean CO2 Ctrl`,
                 `SD CO2 Ctrl`,
                  data=co2_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_co2

sink("co2_results_rand.txt")
print(m_co2)
sink()
```


CH4
```{r}
ch4_dat = sed_flux[,c(1,8,40,41,42,43,44,45)]
ch4_only = sed_flux[complete.cases(ch4_dat),]

m_ch4 <- metacont(`n ch4 oys`,
                 `mean ch4 oys`,
                 `sd ch4 oys`,
                 `n ch4 ctrl`,
                 `mean CH4 ctrl`,
                 `sd CH4 ctrl`,
                  data=ch4_only,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_ch4

sink("ch4_results_rand.txt")
print(m_ch4)
sink()
```



Compare sediment fluxes between C. virginica and C. gigas habitats
```{r}
gigas_nuts = subset(sed_flux, Species == "Crassostrea gigas")
virginica_nuts = subset(sed_flux, Species == "Crassostrea virginica")
nuts_oyster_comp = rbind(gigas_nuts, virginica_nuts)

nuts_oyster_comp_nh4 = na.omit(cbind(nuts_oyster_comp[,1],nuts_oyster_comp[,6], nuts_oyster_comp[,16:21]))

m_species_nh4_comp <- metacont(`n NH4 Oys`,
                 `Mean NH4 Oys`,
                 `SD NH4 Oys`,
                 `n NH4 ctrl`,
                 `Mean NH4 Ctrl`,
                 `SD NH4 Ctrl`,
                  data=nuts_oyster_comp_nh4,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_species_nh4_comp

subgroup.analysis.mixed.effects(m = m_species_nh4_comp, 
                                subgroups = nuts_oyster_comp_nh4$Species)
#the subgroup.analysis.mixed.effects command is in the dmetar file, or the source code can be downloaded here:https://raw.githubusercontent.com/MathiasHarrer/dmetar/master/R/subgroup_analyses_mixed_effects_function.R


nuts_oyster_comp_po4 = na.omit(cbind(nuts_oyster_comp[,1], nuts_oyster_comp[,6],nuts_oyster_comp[,34:39]))
m_oyster_po4_comp <- metacont(`n P Oys`,
                 `Mean P Oys`,
                 `SD P Oys`,
                 `n P Ctrl`,
                 `Mean P Ctrl`,
                 `SD P Ctrl`,
                  data=nuts_oyster_comp_po4,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_oyster_po4_comp

subgroup.analysis.mixed.effects(m = m_oyster_po4_comp, 
                                subgroups = nuts_oyster_comp_po4$Species, exclude = "none")
```


Next compare fluxes between oyster habitats (reef vs. aquaculture):
```{r}
#need to run the next code chunk to load the comparison function

#for comparing N2 fluxes, use just the n2/Ar data
n2_ar_sed = subset(sed_flux, n2_method == "n2_ar")

#next pull out just reef and aqua habitat
reef_n2 = subset(n2_ar_sed, Habitat == "Reef")
aqua_n2 = subset(n2_ar_sed, Habitat == "Aquaculture")

#also need to remove the Ayvazian data for the comparison as it is considered to be an outlier (see publication bias analysis below)
reef_n2 = reef_n2[-c(11),]

n2_comp_dat = rbind(reef_n2, aqua_n2)
n2_comp_dat = as.data.frame(n2_comp_dat)


#re-run the meta-analysis using just these two habitats
m_n2_comp.raw <- metacont(`n N2 Oys`,
                 `Mean N2 Oys`,
                 `SD N2 Oys`,
                 `n N2 Ctrl`,
                 `Mean N2 Ctrl`,
                 `SD N2 Ctrl`,
                  data=n2_comp_dat,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_n2_comp.raw

subgroup.analysis.mixed.effects(m = m_n2_comp.raw, 
                                subgroups = n2_comp_dat$Habitat, exclude = "none")



######### repeat this for NH4 and PO4
reef_nuts = subset(sed_flux, Habitat == "Reef")
aqua_nuts = subset(sed_flux, Habitat == "Aquaculture")
nuts_comp = rbind(reef_nuts, aqua_nuts)

nuts_comp_nh4 = na.omit(cbind(nuts_comp[,1], nuts_comp[,8],nuts_comp[,16:21]))

m_nh4_comp <- metacont(`n NH4 Oys`,
                 `Mean NH4 Oys`,
                 `SD NH4 Oys`,
                 `n NH4 ctrl`,
                 `Mean NH4 Ctrl`,
                 `SD NH4 Ctrl`,
                  data=nuts_comp_nh4,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_nh4_comp

subgroup.analysis.mixed.effects(m = m_nh4_comp, 
                                subgroups = nuts_comp_nh4$Habitat)


nuts_comp_nox = na.omit(cbind(nuts_comp[,1], nuts_comp[,8],nuts_comp[,52:57]))

m_nox_comp <- metacont(`n nox oys`,
                 `mean nox oys`,
                 `sd nox oys`,
                 `n nox ctrl`,
                 `mean nox ctrl`,
                 `sd nox ctrl`,
                  data=nuts_comp_nox,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_nox_comp

subgroup.analysis.mixed.effects(m = m_nox_comp, 
                                subgroups = nuts_comp_nox$Habitat)


nuts_comp_no3 = na.omit(cbind(nuts_comp[,1], nuts_comp[,8],nuts_comp[,58:63]))

m_no3_comp <- metacont(`n no3 oys`,
                 `mean no3 oys`,
                 `sd no3 oys`,
                 `n no3 ctrl`,
                 `mean no3 ctrl`,
                 `sd no3 ctrl`,
                  data=nuts_comp_no3,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_no3_comp

subgroup.analysis.mixed.effects(m = m_no3_comp, 
                                subgroups = nuts_comp_no3$Habitat)



nuts_comp_po4 = na.omit(cbind(nuts_comp[,1], nuts_comp[,8],nuts_comp[,34:39]))
m_po4_comp <- metacont(`n P Oys`,
                 `Mean P Oys`,
                 `SD P Oys`,
                 `n P Ctrl`,
                 `Mean P Ctrl`,
                 `SD P Ctrl`,
                  data=nuts_comp_po4,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_po4_comp

subgroup.analysis.mixed.effects(m = m_po4_comp, 
                                subgroups = nuts_comp_po4$Habitat, exclude = "none")
```



--------------------------------------
Publiction Bias Analysis (based on:https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/publication-bias.html)

load dmetar library
```{r}
library(dmetar)
library(robvis)
library(stringr)
library(poibin)
library(ggrepel)
```

Look for outliers in the N2_Ar meta analysis
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_n2_ar)
#it looks like Ayvazian et al. may be one

#and should we exclude the outlier? USe Eggers test, and if it is significant, yes!
eggers.test(x = m_n2_ar)

#re-run and print model
n2_ar_sed = subset(sed_flux, n2_method == "n2_ar")
n2_ar_sed_no_out =n2_ar_sed[-c(18),]

m_n2_ar_no_out <- metacont(`n N2 Oys`,
                 `Mean N2 Oys`,
                 `SD N2 Oys`,
                 `n N2 Ctrl`,
                 `Mean N2 Ctrl`,
                 `SD N2 Ctrl`,
                  data=n2_ar_sed_no_out,
                  studlab=paste(abbreviated_name),
                  comb.fixed = FALSE, #use fixed effect model?
                  comb.random = TRUE, #use random effect model?
                  method.tau = "SJ", #estimator to use for between study variance (SJ = Sidik-Jonkman)
                  hakn = TRUE, #use Hartung-Knapp-Sidik-Jonkman method?
                  prediction=TRUE,  #generate a 95% prediction interval
                  sm="SMD") #smd indicates we are using Hedges g
m_n2_ar_no_out

#print results in text file
sink("m_n2_ar_no_out.txt")
print(m_n2_ar_no_out)
sink()
```

Look for outliers in the IPT meta analysis
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_n2_ipt)
eggers.test(x = m_n2_ipt)
```

Repeat for NH4
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_nh4)
eggers.test(x = m_nh4)
```

Repeat for NOx
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_nox)
eggers.test(x = m_nox)
```

For NO2
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_no2)
eggers.test(x = m_no2)
```

For NO3
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_no3)
eggers.test(x = m_no3)
```

For PO4
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_po4)
eggers.test(x = m_po4)
```

For DSi
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_si)
eggers.test(x = m_si)
```

For CO2
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_co2)
eggers.test(x = m_co2)
```

For N2O
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_n2o)
eggers.test(x = m_n2o)
```

For CH4
```{r}
#look for outliers based on between study heterogeneity
find.outliers(m_ch4)
eggers.test(x = m_ch4)
```

